GVN-Hoist: Hoisting Computations from Branches

### 2016-08-22 hoist.tex
code-size

TODO: Table for decrease in the code-size of final binaries.

>>>>

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|c|}
      \hline
      Code-size metric  (.text)                   & Number   \\\hline
      Total  benchmarks                           & 497      \\\hline
      Total  gained in size                       & 39       \\\hline
      Total  decrease in size                     & 58       \\\hline
      Median decrease in size                     & 2.9\%    \\\hline
      Median increase in size                     & 2.4\%    \\\hline
    \end{tabular}
  \end{center}
  \caption{Code size metrics on llvm-testsuite}
  \label{tab:code-size}
\end{table}

While benchmarking llvm-testsuite we see both increase as well as decrease in
the codesizes of the final binaries. Since the pass runs early, it has affect on
many optimizations which rely on number of instructions, lenth of the use-def
chain etc metrics which are affected by code-hoisting. Specially the inliner
where the total inline cost (in llvm) is heavily dependent on the total count of
instructions in the caller and callee. Various code-size metrics are shown in
Table-\ref{tab:code-size}. All but one benchmark varied between -5.32\% and
5.43\%.  In one benchmark FreeBench/distray/distray.test, the codesize increased
by 35.38\%.
